Basketball: an analysis of a single game

### 2021-01-27 inst/NBA.Rmd
issue #73

---
title: "Basketball: an analysis of a single game"
output: html_document
---

@@

NBA2_maxp <- maxp(NBA2)
NBA2_maxp %<>% ordertrans(c(colnames(NBA_table)[-(1:4)],"C_possession","W_possession"))
dotchart(NBA2_maxp,col=c(rep("black",9),rep("red",10),rep("blue",2)),pch=16)

NBA_maxp <- maxp(NBA)
NBA_maxp %<>% ordertrans(c(colnames(NBA_table)[-(1:4)],"possession"))
dotchart(NBA_maxp,col=c(rep("black",9),rep("red",10),rep("blue",1)),pch=16)
```

@@

```{r,label=saveNBAdataset}
save(NBA_table,NBA,NBA_maxp,file="NBA.rda")
```

>>>>

--
title: "Basketball: an analysis of a single game"
output: html_document
---

@@

NBA2_maxp <- maxp(NBA2)

NBA2_maxp %<>% ordertrans(c(colnames(NBA_table)[-(1:4)],"C_possession","W_possession"))
dotchart(NBA2_maxp,col=c(rep("black",9),rep("red",10),rep("blue",2)),pch=16)

NBA_maxp_precomputed  <- c(
                                        # precomputed; very very computer
                                        # intensive but far higher likelihood
                                        # than the result of maxp(NBA):

    Barnes     = 0.150357987445096,   Curry       = 1.65443013016506e-06,
    Durant     = 0.00856905879575095, Green       = 0.0253069705861388,
    Iguodala   = 0.00916478949994613, Irving      = 0.0290988580288644, 
    James      = 1.0000039853319e-06, Jefferson   = 0.00446265583190174, 
    Korver     = 0.00959220615914446, Livingston  = 0.0775529739242179, 
    Love       = 0.00253529174567821, McCaw       = 0.0189848298815197,
    Pachiuila  = 0.0365345555046955,
    possession = 0.431812626360354,
    Shumpert   = 0.0556862911754396,   Smith      = 0.00064258717253104,
    Thompson   = 6.86257295623038e-05, Thompson.1 = 0.00824420466131726,
    West       = 0.0761409792438058,   Williams   = 0.0552418538199202)
NBA_maxp <- maxp(NBA)
NBA_maxp %<>% ordertrans(c(colnames(NBA_table)[-(1:4)],"possession"))

dotchart(NBA_maxp,col=c(rep("black",9),rep("red",10),rep("blue",1)),pch=16)
```

@@

```{r,label=saveNBAdataset}
NBA_maxp <- NBA_maxp_precomputed
save(NBA_table,NBA,NBA_maxp,file="NBA.rda")
```
